---
title: "Practice assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


###2.1 Passenger Breakdown
The first step is to convert the array into a data frame using 'data.frame()' function. In this case, I assigned the data frame to "Titanic_data"
```{r echo=TRUE, eval=TRUE}
Titanic_data <- data.frame(Titanic)

```

After that, 2 subset of the data were selected for all the children and adult respectively.
```{r echo=TRUE, eval=TRUE}
Child <- Titanic_data[Titanic_data$Age=="Child",]
Adult <- Titanic_data[Titanic_data$Age=="Adult",]
```

Finally, the 'sum()' function is used to calculate the number Child and Adult on titanic.
```{r echo=TRUE, eval=TRUE}
##the number of Chilren on Titanic:
Child_number <- sum(Child$Freq,na.rm=TRUE)
##the numver of adults on Titanic:
Adult_number <- sum(Adult$Freq,na.rm=TRUE)

Child_number
Adult_number
```

To determine the number of male adult and female adult, I further selected subset from the Adult on Titanic data set previously developed. I then use the 'sum()' function again to calculate the number of male adult and female adult on Titanic.
```{r echo=TRUE, eval=TRUE}
Male_Adult <- Adult[Adult$Sex=="Male",]
Female_Adult <- Adult[Adult$Sex=="Female",]

##the number of male adult on Titanic:
Male_Adult_number <- sum(Male_Adult$Freq,na.rm=TRUE)
##the numver of female adult on Titanic:
Female_Adult_number <- sum(Female_Adult$Freq,na.rm=TRUE)
```


Finally, a 'if' and 'else if' statment is used to print out the result.
```{r echo=TRUE, eval=TRUE}
if(Male_Adult_number > Female_Adult_number){
   print("There are more male adults on Titanic")
} else if (Male_Adult_number < Female_Adult_number){
  print("There are more female adults on Titanic")
} else if(Male_Adult_number == Female_Adult_number){
  print("There are same amount of male and female on Titanic")
}
```


###2.2 Survival Rate
```{r echo=TRUE, eval=TRUE}
Alive_Child <- Child[Child$Survived=="Yes",]
Alive_Child_number <- sum(Alive_Child$Freq,na.rm=TRUE)
Child_Survival_rate = Alive_Child_number/Child_number

Alive_Adult <- Adult[Adult$Survived=="Yes",]
Alive_Adult_number <- sum(Alive_Adult$Freq,na.rm=TRUE)
Adult_Survival_rate = Alive_Adult_number/Adult_number

Child_Survival_rate
Adult_Survival_rate
```

```{r echo=TRUE, eval=TRUE}
if(Adult_Survival_rate > Child_Survival_rate){
   print("Adults have a better survival rate")
} else if (Adult_Survival_rate < Child_Survival_rate){
  print("Children have a better survival rate")
} else if(Adult_Survival_rate == Child_Survival_rate){
  print("The survival rate are same between children and adult")
}
```


```{r echo=TRUE, eval=TRUE}
First_Class <- Titanic_data[Titanic_data$Class=="1st",]
Second_Class <- Titanic_data[Titanic_data$Class=="2nd",]
Third_Class <- Titanic_data[Titanic_data$Class=="3rd",]
Crew <- Titanic_data[Titanic_data$Class=="Crew",]

First_class_number <- sum(First_Class$Freq,na.rm=TRUE)
Second_class_number <- sum(Second_Class$Freq,na.rm=TRUE)
Third_class_number <- sum(Third_Class$Freq,na.rm=TRUE)
Crew_number <- sum(Crew$Freq,na.rm=TRUE)

First_Class_Survived <- First_Class[First_Class$Survived=="Yes",]
Second_Class_Survived <- Second_Class[Second_Class$Survived=="Yes",]
Third_Class_Survived <- Third_Class[Third_Class$Survived=="Yes",]
Crew_Survived <- Crew[Crew$Survived=="Yes",]

First_Class_Survived_number <- sum(First_Class_Survived$Freq,na.rm=TRUE)
Second_Class_Survived_number <- sum(Second_Class_Survived$Freq,na.rm=TRUE)
Third_Class_Survived_number <- sum(Third_Class_Survived$Freq,na.rm=TRUE)
Crew_Survived_number <- sum(Crew_Survived$Freq,na.rm=TRUE)

##First Class Survival rate
First_Class_Survived_number/First_class_number
##2nd class
Second_Class_Survived_number/Second_class_number
##3rd class
Third_Class_Survived_number/Third_class_number
##Crew
Crew_Survived_number/Crew_number
```
