---
title: "Practice assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


###2.1 Passenger Breakdown
The first step is to convert the array into a data frame using 'data.frame()' function. In this case, I assigned the data frame to "Titanic_data"
```{r echo=TRUE, eval=TRUE}
Titanic_data <- data.frame(Titanic)

```

After that, 2 subset of the data were selected for all the children and adult respectively.
```{r echo=TRUE, eval=TRUE}
Child <- Titanic_data[Titanic_data$Age=="Child",]
Adult <- Titanic_data[Titanic_data$Age=="Adult",]
```

Finally, the 'sum()' function is used to calculate the number Child and Adult on titanic.
```{r echo=TRUE, eval=TRUE}
##the number of Chilren on Titanic:
sum(Child$Freq,na.rm=TRUE)
##the numver of adults on Titanic:
sum(Adult$Freq,na.rm=TRUE)
```

To determine the number of male adult and female adult, I further selected subset from the Adult on Titanic data set previously developed. I then use the 'sum()' function again to calculate the number of male adult and female adult on Titanic.
```{r echo=TRUE, eval=TRUE}
Male_Adult <- Adult[Adult$Sex=="Male",]
Female_Adult <- Adult[Adult$Sex=="Female",]

##the number of male adult on Titanic:
Male_Adult_number <- sum(Male_Adult$Freq,na.rm=TRUE)
##the numver of female adult on Titanic:
Female_Adult_number <- sum(Female_Adult$Freq,na.rm=TRUE)
```


Finally, a 'if' and 'else if' statment is used to print out the result.
```{r echo=TRUE, eval=TRUE}

if(Male_Adult_number > Female_Adult_number){
   print("There are more male adults on Titanic")
} else if (Male_Adult_number < Female_Adult_number){
  print("There are more female adults on Titanic")
} else if(Male_Adult_number == Female_Adult_number){
  print("There are same amount of male and female on Titanic")
}
```

